---
title: "Trying for a different tree specification"
output: html_notebook
---

Trying to specify a tree in a better way than using the tibble
like I did in 003.
```{r, message=FALSE}
library(tidyverse)
library(srsStuff)
```

Let's first load in all the individuals and their population designations:
```{r, message=FALSE}
meta <- read_csv("data/wgs-chinoook-samples-cleaned.csv") %>%
  mutate(
    group1 = recode(
      Population,
      "Salmon River Fall" =  "SalmR-Fall",
      "Salmon River Spring" =  "SalmR-Spri",
      "Feather River Hatchery Fall" =  "FeatH-Fall",
      "Feather River Hatchery Spring" =  "FeatH-Spri",
      "Trinity River Hatchery Fall" =  "TrinH-Fall",
      "Trinity River Hatchery Spring" =  "TrinH-Spri",
      "San Joaquin River Fall" =  "SanJo-Fall",
      "Coleman Hatchery Late Fall" =  "ColmH-LFal",
      "Sacramento River Winter" =  "SacrR-Wint",
      "Butte Creek Spring" =  "ButtC-Spri"
    )) %>%
  rename(indiv = vcf_name) %>%
  select(indiv, group1)
```
Now, we can make our tree_list:
```{r}
# get the populations in there
treelist <- split(x = meta$indiv, f = meta$group1)

# now, all the internal nodes
treelist$SalmonR <- c("SalmR-Fall", "SalmR-Spri")
treelist$TrinityH <- c("TrinH-Fall", "TrinH-Spri")
treelist$FeatherH <- c("FeatH-Fall", "FeatH-Spri")
treelist$Klamath <- c("SalmonR", "TrinityH")
treelist$Sacto_F_LF <- c("FeatherH", "ColmH-LFal", "SanJo-Fall")
treelist$Sacramento <- c("Sacto_F_LF", "ButtC-Spri", "SacrR-Wint")
treelist$Root <- c("Sacramento", "Klamath")

```

Check that treelist and looks at the plots of it to confirm it is correct:
```{r}
set.seed(1234)
check_tree <- prepare_treelist(treelist)
```

Here is the plot with no internal node names:
```{r}
check_tree$plots$tree_without_names
```

Here it is with the internal node names on there:
```{r}
check_tree$plots$tree_with_names
```

If you prefer to stare at a classical rooted-looking dendrogram, you can access
them like so:
```{r}
check_tree$plots$dendrogram_without_names
```
Or include the names too:
```{r, fig.width=6}
check_tree$plots$dendrogram_with_names
```

Now, let us also get the individual sample names in the order that they appear
in the VCF file.
```{r}
vcf_names <- read_lines("intermediates/003/sample_names.txt")
```

And then we run prepare treelist again, producing all the necessary input
for `srs_identity()`.
```{r}
prepped_tree <- prepare_treelist(
  treelist,
  vcf_names = vcf_names
)
```
